Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-19 paper/paper.tex
Almost complete the entire draft for the paper

There are multiple platforms for providing such issue tracking systems, among which
the most popular are Jira \cite{jira} and Bugzilla \cite{bugzilla}. For both platforms,
the tickets are split into two main categories: feature requests (i.e. feature to be 
implemented into the system) and bug reports (i.e. issue encountered by an end user or
discovered by a developer in the codebase). Regardless of the type of ticket, they possess
various information that can be filled in by the reporter (i.e. person who created the ticket; 
can be both an end user or a developer in the team), providing the developers
a detailed view of what is requested or what went wrong.

@@

@@

However, we can not automatically change this through automation like the solutions we presented in the previous 
analysis types. We cannot call, for example, the Bing Spell Check API every couple of seconds on the text the user 
is inputting in the ticket as the costs would become unbearable very soon. Thus, what can be done to fix this? It is, 
after all, in the human nature to make mistakes, and typing is no exception. The solution we are proposing implies a 
local, lightweight spell checker that is run automatically as the user types. This tool would not make any external 
calls, so there would be no costs and the load on the server would also be lower. There are already local applications 
that can be used for performing such real-time analysis on the text, one of them being LibreOffice's built-in 
spell checker.

@@

A correlational analysis revealed a weak positive/negative (one of them, depending on context) relationship
with \emph{r} = \dots, \emph{p} = \dots.

>>>>

There are multiple platforms for providing such issue tracking systems, among which
the most popular are Jira and Bugzilla. For both platforms,
the tickets are split into two main categories: feature requests (i.e. feature to be 
implemented into the system) and bug reports (i.e. issue encountered by an end user or
discovered by a developer in the codebase). Regardless of the type of ticket, they possess
various information that can be filled in by the reporter (i.e. person who created the ticket; 
can be both an end user or a developer in the team), providing the developers
a detailed view of what is requested or what went wrong.

@@

%TODO: add a bit more info here and add summary for all analyses (which one is significant, what does each of them imply)

@@

However, we can not automatically change this through automation like the solutions we presented in the previous 
analysis types. We cannot call, for example, the Bing Spell Check API every couple of seconds on the text the user 
is inputting in the ticket as the costs would become unbearable very soon. Thus, what can be done to fix this? It is, 
after all, in the human nature to make mistakes, and typing is no exception. If we, for example, have some hint or a rule
in the code of conduct for the project stating that everything should be 100\% gramatically correct, many reporters not 
having English as their primary language would feel unwelcomed and they might not get involved in the project anymore.

The solution we are proposing implies a local, lightweight spell checker that is run automatically as the user types. 
This tool would not make any external calls, so there would be no costs and the load on the server would also be lower. 
There are already local applications that can be used for performing such real-time analysis on the text, one of them 
being LibreOffice's built-in spell checker.

@@

Sentiment analysis is a technique of employing Machine Learning algorithms in order to infer a sentiment 
score from textual information. These algorithms need to be trained on very large data sets in order to 
produce valuable results. Moreover, we would have also needed an already annotated data set, which means 
a number of strings where we compute the score by hand given a mathematical formula we define. Even though 
there are open source libraries that can help creating and employing the algorithms, such as TensorFlow, 
we would still have needed tickets where we defined what do we mean by positive/negative tickets, as well as
manually computing the scores for a large range of them. Therefore, we ended using a third party API - Google 
Cloud Platform Natural Language Processing, considered the best such service at the moment.

After we concatenated summaries, descriptions and all the comments for every ticket, we started sending our 
requests to Google and we plotted the data shown in Figure \ref{sentiment}. A correlational analysis revealed a 
weak negative relationship with $r = -0.114$, $p < 0.01$. Therefore, we obtained statistically significant 
results implying that as the sentiment decreases (i.e. becomes more negative), the Time-To-Close increases, thus 
decreasing the quality of a ticket.

We can see in the Figure that neutral scores (i.e. between -0.42 and 0.42) show rather neutral results, which 
was expectable: this most probably implies that the discussions and descriptions for these tickets revolved 
completely around the ticket and nothing else.

However, as the sentiment decreases, we can clearly observe that the sentiment scores increase significantly. 
This might signify that once the discussion becomes \"heated\", the developers might lose interest in solving 
the task anymore. Also, rude language might be a driver for increased Times-To-Close because when developers are 
answering questions from the reporters (or vice versa), the other person might become rude or unpolite, which can 
make them feel unwelcomed and start to lose interest in helping the project anymore.

On the other side of the spectrum, having a more positive score leads to higher quality in tickets. Calefato et. al 
\cite{calefato2015mining} conducted a study where they show that a positive sentiment has the biggest impact on 
the quality of an answer on Stack Overflow, one of the most popular websites related to programming in general.
